---
title: "Logistic_Regression_Exercise"
author: "Xu Yang"
date: "12/7/2017"
output: html_document
---

# Regression with binary outcomes
 ═════════════════════════════════

## Logistic regression
 ───────────────────────

   This far we have used the `lm' function to fit our regression models.
   `lm' is great, but limited–in particular it only fits models for
   continuous dependent variables. For categorical dependent variables we
   can use the `glm()' function.

   For these models we will use a different dataset, drawn from the
   National Health Interview Survey. From the [CDC website]:

         The National Health Interview Survey (NHIS) has monitored
         the health of the nation since 1957. NHIS data on a broad
         range of health topics are collected through personal
         household interviews. For over 50 years, the U.S. Census
         Bureau has been the data collection agent for the National
         Health Interview Survey. Survey results have been
         instrumental in providing data to track health status,
         health care access, and progress toward achieving national
         health objectives.

[CDC website] http://www.cdc.gov/nchs/nhis.htm

##   Load the National Health Interview Survey data:

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE,results='hide'}
NH11 <- readRDS("dataSets/NatHealth2011.rds")
labs <- attributes(NH11)$labels
```

## Exercise: logistic regression
 ───────────────────────────────────

   Use the NH11 data set that we loaded earlier.

   1. Use glm to conduct a logistic regression to predict ever worked
      (everwrk) using age (age_p) and marital status (r_maritl).
   2. Predict the probability of working for each level of marital
      status.

   Note that the data is not perfectly clean and ready to be modeled. You
   will need to clean up at least some of the variables before fitting
   the model.
   
## Check and Clean Data

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
summary(NH11$age_p)
```

Age range is from 18 to 85

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
levels(NH11$r_maritl)
summary(NH11$r_maritl)
```

 "0 under 14 years" and "3 Married -spouse in household unknown" don't have any record, so we can remove those two from levels

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
NH11$r_maritl <- factor(NH11$r_maritl)
levels(NH11$r_maritl)
summary(NH11$everwrk)
```

 We just need two levels for 'everwrk' variable.
```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
NH11$everwrk <- factor(NH11$everwrk, levels=c("2 No", "1 Yes"))
```

 Remove those records whose everwrk have a value NA
```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
NH11_2<-NH11[!is.na(NH11$everwrk),]
```

## Generate the logistic regression
```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
everwrk.out <- glm(everwrk~age_p+r_maritl,
               data=NH11_2, family="binomial")
summary(everwrk.out)
```

## Create a dataset group by r_maritl with mean age

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
library(dplyr)
predDat_wrk <-as.data.frame( NH11_2%>%group_by(r_maritl)%>%summarise(age_p=mean(age_p)) )
predDat_wrk
```

## predict everwrk for each level of r_maritl

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
predict_result<-cbind(predDat_wrk, predict(everwrk.out, type = "response",
                       se.fit = TRUE, interval="confidence",
                       newdata = predDat_wrk))
predict_result
```

 predict_result shows that "5 Divorced" has highest probability of working which is 0.9505;
 "Never married" has lowest probability of working which is 0.7673.

## Use the effects package to compute quantities of interest for us (cf. the Zelig package).

```{r eval=TRUE,echo=TRUE,message=FALSE,error=FALSE,warning=FALSE}
library(effects)
plot(allEffects(everwrk.out))
```

